### 2014-03-12 src/results.Rnw
update

The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
the results for line count criteria where the sampling was conducted inside the
program element.

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
@

>>>>

The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
the results for line count criteria where the sampling was conducted inside the
program element. Similaryl the Table~\ref{tbl:onesel} contains the results for
the criteria of one mutant per program element.

Finally Table~\ref{tbl:opsel} contains the results for operator selectionl. Unlike
the other tables, the first column here contains the kind of operator selection
applied. We have tabulated the results of applying particular kinds of operator
selection. The TSDL row is the result of applying only the higher order mutant
equivalent to \textit{statement deletion}. The rows that have prefixes \textit{op:}
are the result of applying only a single mutation operator on the program. The rows
with \textit{opsel:} contains the results of various operator selection mechansisms.
All the \textit{opsel:N-sel} are the results of N-selective operator selection
strategies~\cite{offutt1993anexperimental}. We used the order of operators
determined from Figure~\ref{fig:op} for this purpose.

% \subsection{SDL vs Random selection}
% \begin{figure*}[t]
% <<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% par(mfrow=c(2,2))
% with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
% with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
% with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
% with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
% @
% \label{fig:sdl1}
% \caption{Statement Deletion vs One per line.}
% \end{figure*}
% <<results='asis'>>=
% oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))
% 
% oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
% oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
% @
